Tables in the project

### 2018-08-13 paper/Tables/2by2Table1.tex
individual level fig table added

\caption{\label{tab:unnamed-chunk-4}Fit Criteria for Each Model Specification}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{cccccc}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Number of level 1 classes} \\
\cmidrule(l{2pt}r{2pt}){2-6}
Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
\hspace{1em}No. of free parameters & 14 & 29 & 44 & 59 & 74\\
\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & < 0.0001 & 1e-04 & < 0.0001 & < 0.0001\\
\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Random effects model}}\\
\hspace{1em}2 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
\hspace{1em}\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
\hspace{1em}3 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
\hspace{1em}4 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
\hspace{1em}\hspace{1em}BIC &  & 332086.045 & 331500.318 &  & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.729 & 0.659 &  & \\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}Means (sd), and counts  of the characteristics of different types of days according to carbohydrate intake.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllll}
\hiderowcolors
\toprule
  & High carbohydrate day & Low carbohydrate day & Regular meals day & P value\textsuperscript{*}\\
\midrule
\showrowcolors
Counts & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
Country (\%) &  &  &  & < 0.001\\
\hspace{1em}England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
\hspace{1em}NI & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
\hspace{1em}Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
\hspace{1em}Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
Day of Week (\%) &  &  &  & < 0.001\\
\hspace{1em}Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
\hspace{1em}Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
\hspace{1em}Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
\hspace{1em}Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
\hspace{1em}Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
\hspace{1em}Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
\hspace{1em}Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
\hspace{1em}Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & < 0.001\\
Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & < 0.001\\
Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & < 0.001\\
Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & < 0.001\\
Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & < 0.001\\
Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & < 0.001\\
Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & < 0.001\\
Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & < 0.001\\
Non-milk extrinsic sugar\textsuperscript{\dag} & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & < 0.001\\
Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & < 0.001\\
Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{*} P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the}\\
\multicolumn{5}{l}{means in multiple groups for continuous variables;}\\
\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as:}\\
\end{tabular}
\end{table}

@@

>>>>

\caption{\label{tab:unnamed-chunk-4}Fit Criteria for Each Model Specification}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{cccccc}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Number of level 1 classes} \\
\cmidrule(l{2pt}r{2pt}){2-6}
Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
\hspace{1em}No. of free parameters & 14 & 29 & 44 & 59 & 74\\
\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
\hspace{1em}\hspace{1em}AIC & 347614.612 & 345397.542 & 344166.407 & 343385.883 & 342902.585\\
\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
\hspace{1em}\hspace{1em}aBIC & 347683.601 & 345540.447 & 344383.229 & 343676.621 & 343267.239\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Random effects model}}\\
\hspace{1em}Lo-Mendell-Rubun LRT & -- & < 0.0001 & 1e-04 & < 0.0001 & < 0.0001\\
\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
\hspace{1em}\hspace{1em}2 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
\hspace{1em}\hspace{1em}3 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
\hspace{1em}\hspace{1em}4 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
BIC &  & 332086.045 & 331500.318 &  & \\
Entropy &  & 0.729 & 0.659 &  & \\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}Means (sd), and counts  of the characteristics of different types of days according to carbohydrate intake.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllll}
\hiderowcolors
\toprule
  & High carbohydrate day & Low carbohydrate day & Regular meals day & P value\textsuperscript{*}\\
\midrule
\showrowcolors
Counts & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
Country (\%) &  &  &  & < 0.001\\
\hspace{1em}England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
\hspace{1em}NI & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
\hspace{1em}Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
\hspace{1em}Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
Day of Week (\%) &  &  &  & < 0.001\\
\hspace{1em}Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
\hspace{1em}Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
\hspace{1em}Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
\hspace{1em}Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
\hspace{1em}Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
\hspace{1em}Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
\hspace{1em}Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
\hspace{1em}Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & < 0.001\\
Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & < 0.001\\
Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & < 0.001\\
Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & < 0.001\\
Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & < 0.001\\
Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & < 0.001\\
Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & < 0.001\\
Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & < 0.001\\
Non-milk extrinsic sugar\textsuperscript{\dag} & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & < 0.001\\
Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & < 0.001\\
Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{*} P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the}\\
\multicolumn{5}{l}{means in multiple groups for continuous variables;}\\
\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey,}\\
\multicolumn{5}{l}{glucose, fructose and glucose syrups, sugars added to food and sugars in fruit juices.}\\
\end{tabular}
\end{table}

@@

\section{personal level classes nutrional
table}\label{personal-level-classes-nutrional-table}

\caption{\label{tab:tab-nutri-indi}Weighted means and percentages (95CI) of the nutrients intake according to individual level carbohydrate eating latent classes.}
  & Low carbohydrate eaters (n = 1730) & Moderate carbohydrate eaters (n = 1772) & High carbohydrate eaters (n = 2653) & P value\textsuperscript{*}\\
Total energy intake (kJ) & 7985.8 (7823.3, 8146.295) & 7341.8 (7825.3, 8146.3) & 7677 (7555.8, 7799,8) & < 0.001\\
Carbohydrate intake (g) & 203.8 (199.8, 207.8) & 218.3 (212.9, 223.7) & 233.4 (229.6, 237.2) & < 0.001\\
\hspace{1em}6 am – 9 am & 23.0 (21.8,  24.3) & 11.2 (10.0, 12.3) & 37.9 (36.8, 39.2) & \\
\hspace{1em}Fibre (g) & 1.4 (1.3, 1.5) & 0.6 (0.5, 0.7) & 2.0 (1.9, 2.2) & \\
\hspace{1em}Sugar (g) & 10.2 (9.6, 10.9) & 5.3 (4.8, 5.8) & 19.7 (19.0, 20.4) & \\
\hspace{1em}Non-milk extrinsic sugar\textsuperscript{\dag} & 4.7 (4.3, 5.1) & 3.2 (2.9, 3.6) & 11.1 (10.7, 11.6) & \\
\hspace{1em}Starch (g) & 12.8 (12.0, 13.5) & 5.9 (5.1, 6.6) & 18.3 (17.6, 19.1) & \\
\hspace{1em}9 am – 12 am & 25.1 (23.9, 26.3) & 33.0 (31.4, 34.6) & 26.2 (25.1, 27.2) & \\
\hspace{1em}Fibre (g) & 1.5 (1.4, 1.6) & 1.6 (1.5, 1.7) & 1.3 (1.2, 1.3) & \\
\hspace{1em}Sugar (g) & 11.6 (10.9, 12.3) & 15.7 (14.8, 16.6) & 14.2 (13.6, 14.8) & \\
\hspace{1em}Non-milk extrinsic sugar (g) & 5.7 (5.2, 6.2) & 9.6 (8.9, 10.2) & 8.1 (7.7, 8.5) & \\
\hspace{1em}Starch (g) & 13.5 (12.8, 14.3) & 17.3 (16.4, 18.3) & 11.9 (11.3, 12.6) & \\
\hspace{1em}12 noon – 2 pm & 42.6 (40.9, 44.3) & 38.7 (37.0, 40.4) & 51.6 (50.2, 52.9) & \\
\hspace{1em}Fibre (g) & 3.1 (2.9, 3.2) & 2.3 (2.2, 2.5) & 3.6 (3.5, 3.7) & \\
\hspace{1em}Sugar (g) & 14.7 (14.0, 15.4) & 14.9 (14.0, 15.7) & 19.4 (18.7, 20.0) & \\
\hspace{1em}Non-milk extrinsic sugar (g) & 7.3 (6.7, 7.8) & 9.1 (8.4, 9.8) & 10.3 (9.8, 10.8) & \\
\hspace{1em}Starch (g) & 27.9 (26.6, 29.1) & 23,8 (22.6, 24.9) & 32.2 (31.2, 33.1) & \\
\hspace{1em}2 pm – 5 pm & 25.0 (23.6, 26.4) & 33.6 (31.6, 35.6) & 24.7 (23.6, 25.7) & \\
\hspace{1em}Fibre (g) & 1.6 (1.5, 1.7) & 1.9 (1.7, 2.0) & 1.3 (1.2, 1.4) & \\
\hspace{1em}Sugar (g) & 11.9 (11.3, 12.7) & 14.5 (13.5, 15.5) & 13.4 (12.8, 13.9) & \\
\hspace{1em}Non-milk extrinsic sugar (g) & 6.9 (6.4, 7.5) & 9.9 (9.0, 8.6) & 8.6 (8.2, 9.1) & \\
\hspace{1em}Starch (g) & 13.1 (12.1, 13.9) & 19.1 (17.7, 20.4) & 11.3 (10.6, 11.9) & \\
\hspace{1em}5 pm – 8 pm & 55.9 (54.1, 57.9) & 54.6 (52.1, 57.0) & 62.9 (61.3, 64.4) & \\
\hspace{1em}Fibre (g) & 4.4 (4.2, 4.5) & 3.7 (3.5, 3.9) & 4.9 (4.7, 5.0) & \\
\hspace{1em}Sugar (g) & 18.7 (17.9, 19.5) & 18.6 (17.6, 19.5) & 21.8 (20.9, 22.5) & \\
\hspace{1em}Non-milk extrinsic sugar (g) & 10.2 (9.6, 10.8) & 11.8 (10.9, 12.6) & 12.1 (11.4, 12.7) & \\
\hspace{1em}Starch (g) & 37.3 (35.8, 38.8) & 35.9 (34.1, 37.9) & 41.1 (39.9, 42.2) & \\
\hspace{1em}8 pm – 10 pm & 23.3 (21.9, 24.6) & 29.7 (27.6, 31.7) & 23.7 (22.5, 24.9) & \\
\hspace{1em}Fibre (g) & 1.4 (1.3, 1.6) & 1.6 (1.5, 1.8) & 1.3 (1.5, 1.8) & \\
\hspace{1em}Sugar (g) & 10.9 (10.3, 11.5) & 13.2 (12.2, 14.2) & 12.4 (11.8, 13.0) & \\
\hspace{1em}Non-milk extrinsic sugar (g) & 7.3 (6.8, 7.8) & 9.4 (8.5, 10.4) & 8.3 (7.8, 8.8) & \\
\hspace{1em}Starch (g) & 12.3 (11.4, 13.3) & 16.4 (15.0, 17.8) & 11.3 (10.5, 12.1) & \\
\hspace{1em}10 pm – 6 am & 8.8 (7.7, 9.8) & 17.6 (15.2, 19.9) & 6.4 (5.8, 7.1) & \\
\hspace{1em}Fibre (g) & 0.34 (0.29, 0.39) & 0.74 (0.63, 0.85) & 0.24 (0.21, 0.27) & \\
\hspace{1em}Sugar (g) & 5.3 (4.6, 6.1) & 10.0 (8.6, 11.5) & 4.1 (3.7, 4.5) & \\
\hspace{1em}Non-milk extrinsic sugar (g) & 3.9 (3.3, 4.6) & 7.7 (6.4, 8.9) & 2.9 (2.6, 3.3) & \\
\hspace{1em}Starch (g) & 3.5 (2.9, 3.9) & 7.5 (6.3, 8.8) & 2.3 (1.9, 2.7) & \\
Carbohydrate percent (\%) & 40.6 (40.2, 41.0) & 47.3 (46.8, 47.8) & 48.3 (47.9, 48.6) & < 0.001\\
Protein intake (g) & 79.9 (77.9, 81.8) & 69.3 (67.6, 71.0) & 73.7 (72.5, 74.8) & < 0.001\\
Protein percent (\%) & 17.2 (16.9, 17.5) & 16.3 (16.0, 16.6) & 16.5 (16.3, 16.6) & < 0.001\\
Fat intake (g) & 74.7 (73.1, 76.4) & 63.8 (62.1, 65.5) & 65.7 (64.4, 67.0) & < 0.001\\
Fat percent (\%) & 35.4 (34.9, 35.8) & 32.5 (32.1, 32.9) & 32.0 (31.7, 32.3) & < 0.001\\
Alcohol intake (g) & 20.8 (18.3, 23.2) & 10.7 (9.4, 11.9) & 8.9 (8.1, 9.8) & < 0.001\\
\multicolumn{5}{l}{\textsuperscript{*} P values were obtained from chi-square test for categorical variables, and one-way ANOVA comparing the means in multiple groups for continuous}\\
\multicolumn{5}{l}{variables;}\\
\multicolumn{5}{l}{\textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose and glucose syrups, sugars added}\\
\multicolumn{5}{l}{to food and sugars in fruit juices.}\\
